Modeling trend in temperature volatility using generalized LASSO

### 2018-05-16 nips-2018/paper.tex
updates on paper

\attn{Need a good dummy variable here, it can't be $u$.} Consider the generic optimization problem
$\min_x f(x)+g(Dx)$
where $x\in \mathbb{R}^n$ and $D\in \mathbb{R}^{m\times n}$. Each
iteration of the linearized ADMM
algorithm~\citep{parikh_proximal_2014} for solving this problem 
has the form
\begin{align}
x & \leftarrow \prox_{\mu f} \left(x - (\mu/\rho)D^\top (D x - z + u )\right)\\
z & \leftarrow \prox_{\rho g} \left(z + u\right) \label{eq:linADMM_steps}\\
u & \leftarrow u + D x - z
\end{align}
 where $z,u\in \mathbb{R}^m$ and the proximal operator is defined as
\begin{equation}
 \prox_{\alpha f}(u) = \min_x \,\, \alpha \cdot f(x)+\frac{1}{2} \norm{ x-u}_2^2.
\label{eq:linADMM_prox}
\end{equation}
Clearly,
\eqref{eq:l1tf_var_st} has this form.\attn{What are $\mu$ and $\rho$?}
% The optimization problem 
% form \eqref{eq:linADMM_opt} by defining
% \begin{align}
% & f(x):= \sum_{k} f_k(x_k) := \sum_{k}x_k+y_{k}^2e^{-x_{k}}\\
% & g(z):= \sum_{l} g_l(z_l) := \sum_{l} \lambda_l |z_l|\label{eq:linADMM_fg}\\
% & z = Dx
% \end{align}
% where $y_k$ is the $k^{th}$ entry of the vector whose entries are
% $y_{ijt}$, and $\lambda_l$ is the $l^{th}$ entry of the vector
% $\Lambda^\top=(\lambda_t\textbf{e}_{n_t}^\top|\lambda_s\textbf{e}_{n_s}^\top)$
% (see \autoref{sec:exten}). 
To perform the steps in \eqref{eq:linADMM_steps}, we need to evaluate
$\prox_{\mu f}$ and $\prox_{\rho g}$. Proximal
algorithms are feasible only if these proximal operators can be
evaluated efficiently which, as we show next, is the case for our
problem.

>>>>

\attn{Need a good dummy variable here, it can't be $u$.} Consider the generic optimization problem
$\min_x f(x)+g(Dx)$
where $x\in \mathbb{R}^n$ and $D\in \mathbb{R}^{m\times n}$. Each
iteration of the linearized ADMM
algorithm~\citep{parikh_proximal_2014} for solving this problem 
has the form

\begin{align}
x & \leftarrow \prox_{\mu f} \left(x - (\mu/\rho)D^\top (D x - z + u )\right)\\
z & \leftarrow \prox_{\rho g} \left(z + u\right) \label{eq:linADMM_steps}\\
u & \leftarrow u + D x - z
\end{align}

\noindent where the algorithm parameters $\mu$ and $\rho$ satisfy $0 < \mu < \rho/\norm{D}_2^2$, $z,u\in \mathbb{R}^m$ and the proximal operator is defined as

\begin{equation}
 \prox_{\alpha f}(u) = \min_x \,\, \alpha \cdot f(x)+\frac{1}{2} \norm{ x-u}_2^2.
\label{eq:linADMM_prox}
\end{equation}

\attn{What are $\mu$ and $\rho$?}

\attn{Arash: I explained it above. They are algorithm parameters.}

Clearly, \eqref{eq:l1tf_var_st} has this form necessary for using this algorithm.
% The optimization problem 
% form \eqref{eq:linADMM_opt} by defining
% \begin{align}
% & f(x):= \sum_{k} f_k(x_k) := \sum_{k}x_k+y_{k}^2e^{-x_{k}}\\
% & g(z):= \sum_{l} g_l(z_l) := \sum_{l} \lambda_l |z_l|\label{eq:linADMM_fg}\\
% & z = Dx
% \end{align}
% where $y_k$ is the $k^{th}$ entry of the vector whose entries are
% $y_{ijt}$, and $\lambda_l$ is the $l^{th}$ entry of the vector
% $\Lambda^\top=(\lambda_t\textbf{e}_{n_t}^\top|\lambda_s\textbf{e}_{n_s}^\top)$
% (see \autoref{sec:exten}). 
To perform the steps in \eqref{eq:linADMM_steps}, we need to evaluate
$\prox_{\mu f}$ and $\prox_{\rho g}$. Proximal
algorithms are feasible only if these proximal operators can be
evaluated efficiently which, as we show next, is the case for our
problem.
